%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Originally started off as a template. 
% However has since been modified a considerable amount.
% Deedy CV/Resume
% XeLaTeX Template
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{AMcEnaneyResume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Aidan}{McEnaney}{
    % This sets up the stuff to be displayed along with your name at the top of the page.
    \href{mailto:aidan.mcenaney@maine.edu}{aidan.mcenaney@maine.edu} | \href{https://www.linkedin.com/in/aidan-mcenaney-9807901a7/}{LinkedIn} |  \href{https://github.com/AMcEnaney1}{GitHub}
}

%--------------------------------------------------------------
%	LEFT COLUMN
%--------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

    \subsection{University of Maine}
        \descript{MA in Mathematics | GPA: 3.9}
        \location{Expected May 2025 \\ Orono, ME }

    \sectionspace

    \subsection{University of Maine}

        \descript{BS in Mathematics}
        \descript{Minor in Computer Science}
        \location{May 2023 \\ Orono, ME }

    \sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

    \subsection{Programming}

        \location{Experienced:}
        \textbullet{} Python \textbullet{} Java \textbullet{} C \textbullet{} Bash \textbullet{} R \\
        \location{Familiar:}
        \textbullet{} MATLAB \textbullet{} C++ \textbullet{} SQL \\ 
        \textbullet{} HTML/CSS/JavaScript \textbullet{} TCl \\
        \textbullet{} Lisp \textbullet{} Haskell \textbullet{} BASIC
        
        \sectionspace

    \subsection{APIs}

        \textbullet{} SentinelHub \textbullet{} Sentinelsat \textbullet{} AWS \\
        
        \sectionspace

    \subsection{Operating Systems}
        \textbullet{} Windows \textbullet{} Linux \textbullet{} OSX
        
        \sectionspace

    \subsection{Other}
        \textbullet{} Git \textbullet{} \LaTeX \textbullet{} Django \textbullet{} FastAPI \\
        \textbullet{} JIRA \textbullet{} Docker \& Kubernetes

    \sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

%------------------------------------------------

    \subsection{Computer Science}

        \textbullet{} Data Science \\
        \textbullet{} Object Oriented Programming \\
        \textbullet{} Functional Programming \\
        \textbullet{} Data Structures \& Algorithms \\
        \textbullet{} Computer Architecture \\
        \textbullet{} Artificial Intelligence \\
        
        \sectionspace % Some whitespace after the section

    \subsection{Mathematics}

        \textbullet{} Mathematical Statistics \\
        \textbullet{} Bayesian Statistics \\
        \textbullet{} Mathematical Modeling \\
        \textbullet{} Stochastic Systems \\
        \textbullet{} Monte Carlo Methods \\
        \textbullet{} Differential Equations \\
        \textbullet{} Linear Algebra \\
        \textbullet{} Asymptotic Analysis \\


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

    \runsubsection{Student Consultant}
    \descript{| Zal.ai}

        \location{Jan. 2024 – Present | Orono, ME}
        \vspace{\topsep} % Hacky fix for awkward extra vertical space
        \begin{tightitemize}
            \item Led a team in documenting existing data sources and establishing data integration protocols for a comprehensive database solution.
            \item Designed and implemented a data schema to effectively organize and integrate data from diverse sources, ensuring data consistency and reliability.
            \item Spearheaded the development of a FastAPI-based API for seamless interaction with the integrated database, providing efficient data access and retrieval functionalities.
            \item Coordinated with stakeholders to identify project requirements and prioritize tasks, ensuring alignment with organizational goals and objectives.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Teaching Assistant}
    \descript{| University of Maine, Math Dept.}

        \location{Sept. 2023 - Present | Orono, ME}
        \begin{tightitemize}
            \item Conducted biweekly recitations and weekly office hours, fostering collaborative problem-solving and offering academic support to students.
            \item Provided comprehensive feedback and grading on student assignments, ensuring clarity and consistency in assessment practices.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Math Modeling Intern}
    \descript{| Ferda Farms \& Innovate For Maine}

        \location{June 2023 - Sept. 2023 | Orono, ME}
        \begin{tightitemize}
            \item Performed independent research on current spectrometry and shellfish models in order to develop and implement a mathematical model to predict the movement, location and density of oysters over time, for use for oyster farms.
            \item Worked with several satellite APIs including but not limited to SetninelHub and Sentinelsat to receive and analyze ocean data.
            \item Assisted in Development of website using Django framework with Python.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Student Consultant}
    \descript{| Black Bear Consulting Corps}

        \location{Jan. 2023 – June 2023 | Orono, ME}
        \begin{tightitemize}
            \item Collaborated with a Maine-based oyster farm to develop customized software aimed at enhancing inspection and reporting processes, optimizing operational efficiency, and compliance.
            \item Designed and implemented a user-friendly website and database tailored to the specific needs and requirements of the oyster farm, facilitating data management and accessibility.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Undergraduate Research Assistant}
    \descript{| CompuMAINE Lab}

        \location{July 2022 – June 2023 | Orono, ME}
        \begin{tightitemize}
            \item Worked on updating and improving upon the lab's image analysis code for use in cancer detection.
            \item Engaged in research activities and attended presentations to support the work of fellow lab members.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------


    \runsubsection{Web Developer}
    \descript{| Franco American Centre}

        \location{Dec. 2021 – Sept. 2022 | Orono, ME}
        \begin{tightitemize}
            \item Worked on a team as a part of a multi-university collaboration to build a digital research tool for Franco American archives.
            \item Managed a wide variety of projects including but not limited to: Audio Archival, Cross-College Communication, Computer Management, and Social Media Management.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section
        
        % Don't actually need this last sectionspace as is this is the last entry, just here for consistency and so the page doesn't get too full. 

%--------------------------------------------------------------

\end{minipage} % The end of the right column

\end{document}