%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Aidan's Resume},
    pdfpagemode=FullScreen,
}

\begin{document}


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Aidan}{McEnaney}{
\href{mailto:aidan.mcenaney@maine.edu}{aidan.mcenaney@maine.edu} | \href{https://www.linkedin.com/in/aidan-mcenaney-9807901a7/}{LinkedIn} |  \href{https://github.com/AMcEnaney1}{GitHub}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{University of Maine}
\descript{MA in Mathematics}
\location{Expected May 2025 \\ Orono, ME }

\sectionspace

\subsection{University of Maine}

\descript{BS in Mathematics}
\descript{Minor in Computer Science}
\location{May 2023 \\ Orono, ME }

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Experienced:}
\textbullet{} Python \textbullet{} Java \textbullet{} R \textbullet{} BASH \\
\location{Familiar:}
\textbullet{} C \textbullet{} MATLAB \textbullet{} C++ \textbullet{} SQL \\ 
\textbullet{} HTML/CSS/JavaScript \textbullet{} TCl
\sectionspace

\subsection{APIs}

\textbullet{} SentinelHub \textbullet{} Sentinelsat
\sectionspace

\subsection{Operating Systems}
\textbullet{} Windows \textbullet{} Ubuntu \textbullet{} OSX
\sectionspace

\subsection{Other}
\textbullet{} Git \textbullet{} STAC \textbullet{} Django \textbullet{} \LaTeX \\ \textbullet{} Geospatial Data Analysis \\ 
\textbullet{} JIRA \textbullet{} Docker \& kubernetes



\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

%------------------------------------------------

\subsection{Computer Science}

\textbullet{} Data Science \\
\textbullet{} Object Oriented Programming \\
\textbullet{} Data Structures \\
\textbullet{} Algorithms \\
\textbullet{} Programming in Python \\
\textbullet{} Advanced C Programming \\
\textbullet{} R programming \\

\sectionspace % Some whitespace after the section

\subsection{Mathematics}

\textbullet{} Differential Equations \\
\textbullet{} Linear Algebra \\
\textbullet{} Mathematical Modeling \\
\textbullet{} Asymptotic Analysis \\
\textbullet{} Stochastic Systems \\
\textbullet{} Monte Carlo Methods \\

\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Ferda Farms/Innovate For Maine }
\descript{| Math Modeling Intern}

\location{June 2023 - Present | Orono, ME}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed and implemented a mathematical model to predict the movement, location and density of oysters over time for use for oyster farms.
\item Worked with several satellite APIs including but not limited to 
SetninelHub and Sentinelsat to receive and analyze ocean data.
\item Assisted in Development of website using Django framework with Python.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Black Bear Consulting Corps}
\descript{| Student Consultant}

\location{January 2023 – June 2023 | Orono, ME}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Worked closely with a Maine company to create software to aid in the inspection and reporting for oyster farms in Maine.
\item Created a website and database for said company based on required specifications.
\item Created marketing material and adjusted website for PowerWise, a company in the solar industry.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{CompuMAINE Lab}
\descript{| Research Assistant}

\location{July 2022 – June 2023 | Orono, ME}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Updated existing code, performing image analysis for broader community use.
\item Attended several meetings on a weekly basis.
\item Worked with other members of lab on current projects.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{University of Maine Math Dept.}
\descript{| Grader}

\location{Sept. 2021 – Jan. 2022, Sept. 2022 - Dec. 2022 | Orono, ME}
\begin{tightitemize}
\item Graded 100+ assignments a week for two different semesters.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{University of Maine Rise Center.}
\descript{| Teaching Assistant}

\location{Sept. 2020 – Dec. 2022 | Orono, ME}
\begin{tightitemize}
\item Assisted in leading recitations and held office hours, as an undergraduate teaching assistant for Calc II.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Franco American Centre}
\descript{| Web Developer, Project Manager}

\location{Dec. 2021 – Sept. 2022 | Orono, ME}
\begin{tightitemize}
\item Worked as the go to IT and tech person in the centre.
\item Managed a wide variety of projects at the Centre, including but not limited to: Audio Archival, Cross-College Communication, Computer Management, and Social Media Management.
\item Assisted in updating code for their old archive website.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Foster Center for Innovation}
\descript{| Software Engineer Intern}

\location{June 2022 – Aug. 2022 | Orono, ME}
\begin{tightitemize}
\item Developed and researched various algorithms.
\item Set up various docker containers to test scripts and algorithms. 
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column


\end{document}