\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
% Fixes warning caused by using hyperef with the moderncv document type
% See here: https://tex.stackexchange.com/questions/34910/avoid-hyperref-warnings-in-moderncv

\documentclass[12pt,letterpaper,unicode]{moderncv}

\moderncvtheme{classic}

\usepackage[hmargin=2cm, vmargin=1.75cm, headheight=14.5pt]{geometry}
\usepackage[unicode]{hyperref} % To use hyperlinks
\usepackage{fancyhdr} % To customize headers and footers

\AtBeginDocument{\recomputelengths}

% Define fancy headers and footers
\pagestyle{fancy}
\fancyhf{} % Clear header and footer
\rhead{\textit{Last updated: \today}} % Set text to the top right corner
\renewcommand{\headrulewidth}{0pt} % Remove header rule line

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Aidan's Resume},
    pdfpagemode=FullScreen,
}

\firstname{Aidan}
\familyname{McEnaney}
\address{}{Orono, ME}
\email{aidan.mcenaney@maine.edu}
\social[linkedin][www.linkedin.com/in/aidan-mcenaney-9807901a7/]{Aidan McEnaney}
\social[github][github.com/AMcEnaney1]{AMcEnaney1}

\nopagenumbers{}                    

\begin{document}
\vspace*{-7mm}
\maketitle
\vspace*{-7mm}

%\lastupdated % Print the Last Updated text at the top right

\section{Employment}
    \cventry{2024-present}{Student Consultant}{Zal.ai}{}{}{
    \begin{itemize}
        \item Led a team in documenting existing data sources and establishing data integration protocols for a comprehensive database solution.
        \item Designed and implemented a data schema to effectively organize and integrate data from diverse sources, ensuring data consistency and reliability.
        \item Spearheaded the development of a FastAPI-based API for seamless interaction with the integrated database, providing efficient data access and retrieval functionalities.
        \item Coordinated with stakeholders to identify project requirements and prioritize tasks, ensuring alignment with organizational goals and objectives.
    \end{itemize}
    }
    \cventry{2023-present}{Teaching Assistant}{University of Maine}{Math Dept.}{}{
    \begin{itemize}
        \item Conducted biweekly recitations and weekly office hours, fostering collaborative problem-solving and offering academic support to students.
        \item Provided comprehensive feedback and grading on student assignments, ensuring \\clarity and consistency in assessment practices.
    \end{itemize}
    }
    \cventry{2023-2023}{Math Modeling Intern}{Innovate For Maine}{Ferda Farms}{}{
    \begin{itemize}
        \item Performed independent research on current spectrometry and shellfish models in order to develop and implement a mathematical model to predict the movement, location and density of oysters over time, for use for oyster farms.
        \item Worked with several satellite APIs including but not limited to SetninelHub and Sentinelsat to receive and analyze ocean data.
        \item Assisted in Development of website using Django framework with Python.
    \end{itemize}
    }
    \cventry{2022-2023}{Undergraduate Research Assistant}{CompuMAINE Lab}{}{}{
    \begin{itemize}
        \item Worked on updating and improving upon the lab's image analysis code for use in cancer detection.
        \item Engaged in research activities and attended presentations to support the work of fellow lab members.
    \end{itemize}
    }

\section{Skills}
    \cvline{Skills}{Statistics, Data Science, Machine Learning}
    \cvline{Languages}{
      Python, Java, C, Bash, R, MATLAB, C++, SQL, Lisp
    }

\section{Education}
    \cventry{2025}{Master of Arts in Mathematics}{University of Maine}{}{}{}
    \cventry{2023}{Bachelor of Science in Mathematics}{University of Maine}{}{}{}

\end{document}