%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Originally started off as a template. 
% However has since been modified a considerable amount.
% Deedy CV/Resume
% XeLaTeX Template
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{resume_AMcEnaney} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Aidan}{McEnaney}{
    % This sets up the stuff to be displayed along with your name at the top of the page.
    \href{mailto:aidan.mcenaney@maine.edu}{aidan.mcenaney@maine.edu} | \href{https://www.linkedin.com/in/aidan-mcenaney-9807901a7/}{LinkedIn} |  \href{https://github.com/AMcEnaney1}{GitHub}
}

%--------------------------------------------------------------
%	LEFT COLUMN
%--------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

    \subsection{University of Maine}
        \descript{MA in Mathematics | GPA: 3.9}
        \location{Expected May 2025 \\ Orono, ME }

    \sectionspace

    \subsection{University of Maine}

        \descript{BS in Mathematics}
        \descript{Minor in Computer Science}
        \location{May 2023 \\ Orono, ME }

    \sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

    \subsection{Programming}

        \location{Experienced:}
        \textbullet{} Python \textbullet{} Java \textbullet{} C \textbullet{} Bash \textbullet{} R \\
        \location{Familiar:}
        \textbullet{} C \textbullet{} MATLAB \textbullet{} C++ \textbullet{} SQL \\ 
        \textbullet{} HTML/CSS/JavaScript \textbullet{} TCl \\
        \textbullet{} Lisp \textbullet{} Haskell \textbullet{} BASIC
        
        \sectionspace

    \subsection{APIs}

        \textbullet{} SentinelHub \textbullet{} Sentinelsat \textbullet{} AWS
        
        \sectionspace

    \subsection{Operating Systems}
        \textbullet{} Windows \textbullet{} Linux \textbullet{} OSX
        
        \sectionspace

    \subsection{Other}
        \textbullet{} Git \textbullet{} STAC \textbullet{} Django \textbullet{} \LaTeX \\ \textbullet{} Geospatial Data Analysis \\ 
        \textbullet{} JIRA \textbullet{} Docker \& Kubernetes

    \sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

%------------------------------------------------

    \subsection{Computer Science}

        \textbullet{} Data Science \\
        \textbullet{} Object Oriented Programming \\
        \textbullet{} Functional Programming \\
        \textbullet{} Data Structures \& Algorithms \\
        \textbullet{} Computer Architecture \\
        \textbullet{} Artificial Intelligence \\
        
        \sectionspace % Some whitespace after the section

    \subsection{Mathematics}

        \textbullet{} Mathematical Statistics \\
        \textbullet{} Bayesian Statistics \\
        \textbullet{} Mathematical Modeling \\
        \textbullet{} Stochastic Systems \\
        \textbullet{} Monte Carlo Methods \\
        \textbullet{} Differential Equations \\
        \textbullet{} Linear Algebra \\
        \textbullet{} Asymptotic Analysis \\


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

    \runsubsection{Student Consultant}
    \descript{| Zal.ai}

        \location{Jan. 2023 – Present | Orono, ME}
        \vspace{\topsep} % Hacky fix for awkward extra vertical space
        \begin{tightitemize}
            \item Assisted in creating an AI and LLM to provide career advice to users.
            \item Collaborated with cross-functional teams to develop and implement AI-powered solutions for real-world business challenges.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Teaching Assistant}
    \descript{| University of Maine, Math Dept.}

        \location{Sept. 2023 - Present | Orono, ME}
        \begin{tightitemize}
            \item Lead biweekly recitations, a structured time for students to work on problems as a group.
            \item Held weekly office hours in the math department's help center.
            \item Gave feedback and graded student's homework and group work.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Math Modeling Intern}
    \descript{| Ferda Farms \& Innovate For Maine}

        \location{June 2023 - Sept. 2023 | Orono, ME}
        \begin{tightitemize}
            \item Performed independent research on current spectrometry and shellfish models in order to develop and implement a mathematical model to predict the movement, location and density of oysters over time, for use for oyster farms.
            \item Worked with several satellite APIs including but not limited to SetninelHub and Sentinelsat to receive and analyze ocean data.
            \item Assisted in Development of website using Django framework with Python.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Student Consultant}
    \descript{| Black Bear Consulting Corps}

        \location{Jan. 2023 – June 2023 | Orono, ME}
        \begin{tightitemize}
            \item Worked closely with a Maine based oyster farm to create software to aid in the inspection and reporting for oyster farms in Maine.
            \item Created a website and database for said company based on required specifications.
            \item Created marketing material and worked on the website for PowerWise, a company in the solar industry.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Undergraduate Research Assistant}
    \descript{| CompuMAINE Lab}

        \location{July 2022 – June 2023 | Orono, ME}
        \begin{tightitemize}
            \item Worked on updating and improving upon the lab's image analysis code for use in cancer detection.
            \item Attended presentations for and participated in research for other lab members.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------


    \runsubsection{Web Developer}
    \descript{| Franco American Centre}

        \location{Dec. 2021 – Sept. 2022 | Orono, ME}
        \begin{tightitemize}
            \item Worked on a team as a part of a multi-university collaboration to build a digital research tool for Franco American archives.
            \item Worked as the sole IT technician for the department.
            \item Managed a wide variety of projects including but not limited to: Audio Archival, Cross-College Communication, Computer Management, and Social Media Management.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section

%------------------------------------------------

    \runsubsection{Software Development Intern}
    \descript{| Innovate For Maine}

        \location{June 2022 – Aug. 2022 | Orono, ME}
        \begin{tightitemize}
            \item Performed extensive research in various fields in order to develop algorithms and products for a multitude of companies with whom we had partnered with.
            \item Created and set up quickstart environments for our clients using ocker and kubernetes.
        \end{tightitemize}

        \sectionspace % Some whitespace after the section
        
        % Don't actually need this last sectionspace as is this is the last entry, just here for consistency and so the page doesn't get too full. 

%--------------------------------------------------------------

\end{minipage} % The end of the right column

\end{document}